Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-06 Latex Source/paper.tex
compiler got mad at citations

\section{Introduction}
This project will focus on people's ability to type with distractions such as different types of music playing. 
It will then test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy. 
The two-part test aims to help test if the music is too distracting or will help the people be more efficient at their work. 
This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors. According to the arousal-mood hypothesis, changes in arousal and mood when exposed to auditory stimulation can influence cognitive function \cite{Chee}.
The two-part test will help determine if there is a correlation between the effectiveness of music versus no music on cognitive response time and typing efficiency.

\subsection{Eye Tracking}
Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements \cite{Rana8642988}. 
In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
The EyeWriter 2.0 offers high-resolution tracking, accurately capturing gaze patterns and fixations.
As Chen \cite{Chen23876} points out while exploring the relationships between distractibility and Eye Tracking during online learning assessments they found significant differences between more distractions meant more distracted eyes. We believe by analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.

\subsection{QBTest}
The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. It is usually used to diagnose ADHD in adults and children as mentioned by \cite{Stevanovic} Stevanovic in their study of 'The Structure and Diagnostic Accuracy of the QbTest in Pediatric ADHD.
Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks fairly accurately. It is also important to understand that it is not completely accurate as discussed by Hult \cite{Hult}.
Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.

\subsection{Typing Test}
Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. 
However, various factors can influence typing efficiency, including environmental stimuli such as music Silverberg \cite{AudioDistractionsAshley} found that the results of their typing test showed that although there was a significant difference in the times between paragraphs, there were no significant differences in typing speed between the audio distractions being played. Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
This study uses a typing test to assess participants' typing performance under different music conditions. 
The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency. 
This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.

@@

\subsection[short]{Design}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest}a. The participants saw Figure \ref*{typingTest}b while the test was running, while Figure \ref*{typingTest}c was the signifier that the typing portion was finished.

@@

@@

Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions. 
While the participants did the cognitive task of a quantified behavioral test, their eye movement will be tracked by the EyeWriter 2.0 camera that we specially built for this study. 
The EyeWriter system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration. This can be seen in Figure \ref*{EyeWriter}.

>>>>

\section{Introduction}
This project will focus on people's ability to type with distractions such as different types of music playing. 
It will then test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy. 
The two-part test aims to help test if the music is too distracting or will help the people be more efficient at their work. 
This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors. 
According to the arousal-mood hypothesis, changes in arousal and mood when exposed to auditory stimulation can influence cognitive function~\cite{Chee}.
The two-part test will help determine if there is a correlation between the effectiveness of music versus no music on cognitive response time and typing efficiency.

\subsection{Eye Tracking}
Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements~\cite{Rana8642988}. 
In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
The EyeWriter 2.0 offers high-resolution tracking, accurately capturing gaze patterns and fixations.
As Chen~\cite{Chen23876} points out while exploring the relationships between distractibility and Eye Tracking during online learning assessments they found significant differences between more distractions meant more distracted eyes. We believe by analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.

\subsection{QBTest}
The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. 
It is usually used to diagnose ADHD in adults and children as mentioned by~\cite{Stevanovic} Stevanovic in their study of 'The Structure and Diagnostic Accuracy of the QbTest in Pediatric ADHD.
Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks fairly accurately. 
It is also important to understand that it is not completely accurate as discussed by Hult~\cite{Hult}.
Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.

\subsection{Typing Test}
Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. 
However, various factors can influence typing efficiency, including environmental stimuli such as music Silverberg~\cite{AudioDistractionsAshley} found that the results of their typing test showed that although there was a significant difference in the times between paragraphs, there were no significant differences in typing speed between the audio distractions being played. 
Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
This study uses a typing test to assess participants' typing performance under different music conditions. 
The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency. 
This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.

@@

\subsection[short]{Design}

@@

After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest}a. The participants saw Figure \ref*{typingTest}b while the test was running, while Figure \ref*{typingTest}c was the signifier that the typing portion was finished.

@@

Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions. 
While the participants did the cognitive task of a quantified behavioral test, their eye movement will be tracked by the EyeWriter 2.0 camera that we specially built for this study. 
The EyeWriter 2.0 system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration. This can be seen in Figure \ref*{EyeWriter}.
